An example exploratory analysis script

### 2024-02-21 code/eda-code/eda.qmd
Part 2 Updates
Removed 2 template files that we did not need. Explored the outliers in the total_BCmethod variables.

Percent of unintended pregnancies is the main outcome of interest, so we will explore this variable first.

```{r}
p1 <- mydata %>% ggplot(aes(x=pct_upreg)) + 
  geom_histogram() + 
  labs(x="Percent of Unintended Pregnancies", y="Frequency at Country Level")
plot(p1)
figure_file = here("results", "figures", "exploratory-figures", "pctupreg_distribution.png")
ggsave(filename = figure_file, plot=p1) 
```

@@

probably skewed by population size 
```{r}
p6 <- mydata %>% ggplot(aes(x=total_larcster)) + geom_histogram(binwidth = 5000) 
plot(p6)
figure_file = here("results", "figures", "exploratory-figures", "total_larcster_distribution.png")
ggsave(filename = figure_file, plot=p6)

@@

>>>>

@@

probably skewed by population size 
```{r}
p6 <- mydata %>% ggplot(aes(x=total_larcster)) + geom_histogram() 
plot(p6)
figure_file = here("results", "figures", "exploratory-figures", "total_larcster_distribution.png")
ggsave(filename = figure_file, plot=p6)

@@

We need to explore where the outliers in these variables are coming from. 
```{r}
outliers <- mydata %>% filter(total_larcster > 25000)
```
